A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-08 main.tex
Example 2
Samma skala för alla automator

    \includegraphics[width=\textwidth]{aca_or_bc}

@@

    \includegraphics[width=\textwidth]{something_c_something}

@@

    \includegraphics[width=\textwidth]{aca_or_bc_simplified}

@@

    \includegraphics[width=\textwidth]{something_c_something_length_simplified}

@@

      \includegraphics[width=\textwidth]{aca_or_bc_length_split_1}

@@

      \includegraphics[width=\textwidth]{aca_or_bc_length_split_2}

@@

      \includegraphics[width=\textwidth]{length_split_product}

@@

      \includegraphics[width=\textwidth]{aca_or_bc_simplified_3}

@@

        \includegraphics[width=\textwidth]{aca_or_bc_times_something_c_something}

@@

In the derivation tree of \cref{fig:derivation:multi} we start as before, but
with the product version of the $\Image$ predicate. The only possible rule here
is $\ExpandM$, which we use to add the corresponding constraints on each
automata of the product as we would have had in the single-automaton version. We
perform algebraic reasoning on those equations, along with the constraint on
$\MonoidElement$ to determine bounds on transition variables that will enable us
to \Subsume{} and remove one of the $\Connected{}$ predicates. When we have
finished doing so, we use \Materialise{} to compute the product of the now
filtered automata. Further algebraic reasoning allows us to remove the final
instance of $\Connected$. We then perform \Expand{} to get rid of the final
$\Image$ instance, and are immediately able to $\Subsume$ the resulting
$\Connected{}$ predicate. This, again, leaves us with a set of linear
inequalities at the leaf that we can use to obtain a model of our final
$\MonoidElement$ values (now a vector).

>>>>

    \includegraphics[scale=\autscale]{aca_or_bc}

@@

    \includegraphics[scale=\autscale]{something_c_something}

@@

    \includegraphics[scale=\autscale]{aca_or_bc_simplified}

@@

    \includegraphics[scale=\autscale]{something_c_something_length_simplified}

@@

      \includegraphics[scale=\autscale]{aca_or_bc_length_split_1}

@@

      \includegraphics[scale=\autscale]{aca_or_bc_length_split_2}

@@

      \includegraphics[scale=\autscale]{length_split_product}

@@

      \includegraphics[scale=\autscale]{aca_or_bc_simplified_3}

@@

        \includegraphics[scale=\autscale]{aca_or_bc_times_something_c_something}

@@

In the derivation tree of \cref{fig:derivation:multi} we start as before, but
with the product version of the $\Image$ predicate. The only possible rule here
is $\ExpandM$, which we use to add the corresponding constraints on each
automata of the product as we would have had in the single-automaton version. We
perform algebraic reasoning on those equations, along with the constraint on
$\MonoidElement$ to determine bounds on transition variables that will enable us
to \Subsume{} and remove one of the $\Connected{}$ predicates. When we have
finished doing so, we use \Materialise{} to compute the product of the now
filtered automata. Further algebraic reasoning allows us to remove the final
instance of $\Connected$. We then perform \Expand{} to get rid of the final
$\Image$ instance, and are immediately able to $\Subsume$ the resulting
$\Connected{}$ predicate. This, again, leaves us with a set of linear
inequalities at the leaf that we can use to obtain a model of our final
$\MonoidElement$ values (now a vector). This time we can read out aca, or
$\VectorLiteral{2, 0, 1}$.
